Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-04-30 TEBenchmarkPaper/article.tex
More fixes

% FIXME: Add section references to the braces
% FIXME: Maybe rethink "analysis" bit; maybe add summary and comparison
% references (although maybe not as full blown steps)
\begin{figure}
  \tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm,
                           minimum height=1cm,text centered, draw=black]

@@

\section{Application}
\label{sec:application}
% FIXME: Maybe use (red?) crosses rather than red dots? More useful for black and white
We have applied our benchmarking methodology to the QuickSpec and IsaCoSy MTE
tools, using version 0.2 of the TIP (Tons of Inductive Problems) theorem proving
benchmark as our ground truth corpus~\cite{claessen2015tip}.

@@

\subsection{TIP} % FIXME: Expand acronym

We chose TIP for our ground truth since it satisfies the desiderata of
$\S$\ref{section:prep}: each benchmark problem has standalone type and function
definitions, making their separation trivial; known examples from the software
verification and inductive theorem proving literature are included, ensuring
relevance to those fields; the format includes the higher-order functions and
inductive datatypes we are interested in; it is large enough to pose a challenge
to current MTE tools; plus it is accompanied by tooling to convert its custom
format (an extension of SMT-Lib~\cite{BarFT-SMTLIB}) into a variety of
languages, including Haskell and Isabelle.

@@

\begin{figure}
  \centering
  \input{quickspectime.pgf}
  \caption{Running times of QuickSpec on theories sampled from TIP. Each point
    is an individual run, with 31 per size except for 1 (14) and 2 (30). Colour
    indicates the total number of conjectures produced by each run, with failing
    processes shown in red. Points are spread out horizontally to prevent
    overlaps. Box plots show median and quartiles, with whiskers showing points
    at 1.5$\times$~inter-quartile range.}
  \label{figure:quickspec_runtimes}
\end{figure}

\begin{figure}
  \centering
  \input{quickspecprec.pgf}
  \caption{Precision and recall of successful QuickSpec runs (spread
    horizontally to avoid overlaps). Point colour shows how many conjectures
    were in the ground truth set for each run. Lines show the combined
    proportion for each sample size (ratio of averages) and the shaded region is
    the sample standard deviation.}
  \label{figure:quickspec_precRec}
\end{figure}

@@

\begin{figure}
  \centering
  \input{isacosytime.pgf}
  \caption{Running times of IsaCoSy on theories sampled from TIP. Each point
    is an individual run, with 31 per size except for 1 (14) and 2 (30). Colour
    indicates the total number of conjectures produced by each run, with failing
    processes (timeouts and out of memory) shown in red. Points are spread out
    horizontally to prevent overlaps. Box plots show median and quartiles, with
    whiskers showing points at 1.5$\times$~inter-quartile range.}
  \label{figure:isacosy_runtimes}
\end{figure}

\begin{figure}
  \centering
  \input{isacosyprec.pgf}
  \caption{Precision and recall of all successful IsaCoSy runs (spread
    horizontally to avoid overlaps). Lines show the combined proportion for each
    sample size (ratio of averages) and the shaded region is the sample standard
    deviation.}
  \label{figure:isacosy_precRec}
\end{figure}

>>>>

% FIXME: Maybe rethink "analysis" bit; maybe add summary and comparison
% references (although maybe not as full blown steps)
\begin{figure}
  \tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm,
                           minimum height=1cm,text centered, draw=black]

@@

\section{Application}
\label{sec:application}

We have applied our benchmarking methodology to the QuickSpec and IsaCoSy MTE
tools, using version 0.2 of the TIP (Tons of Inductive Problems) theorem proving
benchmark as our ground truth corpus~\cite{claessen2015tip}.

@@

\subsection{Tons of Inductive Problems}

We chose the Tons of Inductive Problems (TIP) benchmark for our ground truth
since it satisfies the desiderata of $\S$\ref{section:prep}: each benchmark
problem has standalone type and function definitions, making their separation
trivial; known examples from the software verification and inductive theorem
proving literature are included, ensuring relevance to those fields; the format
includes the higher-order functions and inductive datatypes we are interested
in; it is large enough to pose a challenge to current MTE tools; plus it is
accompanied by tooling to convert its custom format (an extension of
SMT-Lib~\cite{BarFT-SMTLIB}) into a variety of languages, including Haskell and
Isabelle.

@@

\begin{figure}
  \centering
  \input{quickspectime.pgf}
  \caption{Running times of QuickSpec on theories sampled from TIP. Each point
    is an individual run, with 31 per size except for 1 (14) and 2 (30). Failing
    processes (timeouts or out-of-memory) are shown in red. Points are spread
    out horizontally to reduce overlapping. Box plots show median and quartiles,
    with whiskers showing points at 1.5$\times$~inter-quartile range.}
  \label{figure:quickspec_runtimes}
\end{figure}

\begin{figure}
  \centering
  \input{quickspecprec.pgf}
  \caption{Precision and recall of successful QuickSpec runs (spread
    horizontally to reduce overlapping). Lines show the combined proportion for
    each sample size (ratio of averages) and errorbars show the sample standard
    deviation.}
  \label{figure:quickspec_precRec}
\end{figure}

@@

\begin{figure}
  \centering
  \input{isacosytime.pgf}
  \caption{Running times of IsaCoSy on theories sampled from TIP. Each point
    is an individual run, with 31 per size except for 1 (14) and 2 (30). Failing
    processes (timeouts and out of memory) are shown in red. Points are spread
    out horizontally to reduce overlapping. Box plots show median and quartiles,
    with whiskers showing points at 1.5$\times$~inter-quartile range.}
  \label{figure:isacosy_runtimes}
\end{figure}

\begin{figure}
  \centering
  \input{isacosyprec.pgf}
  \caption{Precision and recall of all successful IsaCoSy runs (spread
    horizontally to reduce overlapping). Lines show the combined proportion for
    each sample size (ratio of averages) and errorbars show the sample standard
    deviation.}
  \label{figure:isacosy_precRec}
\end{figure}
